Secure Multi-Party Computation with SCALE-MAMBA

### 2019-04-14 paper.tex
small progress

\subsection{Shamirs Secret Sharing Scheme}
This paper will not further discuss the family of garbled circuit protocols, but rather the second family which are protocols based on so called Linear Secret Sharing. 
These type of protocols were introduced by Adi Shamir at a similar time, in 1979 \cite{Shamir:1979:SS:359168.359176}.\\
The basic idea of this approach is that multiple parties split their secrets into so called shares and then distribute them to the other parties. In Shamir's scheme this is done by generating random polynomials with a degree depending on the security level and then calculating the shares as points in this polynomial. Computations are executed on these shares, and at the end it is possible to reconstruct the result from the different shares without revealing information about the initial secrets. This is done by using Lagrange interpolation.\\
 There is a huge family of protocols build on this approach, and it is still evolving every day. This paper will focus on the newest of these protocols that were developed in the last 10 years, especially on the SPDZ like protocols.\\

@@

@@

Now we assume that the offline phase was succesfully executed, so all preliminaries are given to execute the online phase. It's main goal is to evaluate a specified circuit with secret inputs by the different parties. So this is the heart of the system, the part where the real computatiuon is executed. \\
It is important to note, that the online phase is nearly perfectly optimized when assuming the offline phase was carried out succesfully. The online phase has a runtime complexity in O(n), and therefore there is not a really big performance impact. It is also noteworthy, that in the online phase only only computational and no information theoretical problems are solved. All this leads to the fact, that there is not really any change in the online phase in the SPDZ like protocols in the last years, therefore the online phase is the same like in the earlier version of SPDZ ~\cite{cryptoeprint:2011:535}.\\

@@

Following, it is going to be demonstrated, how addition and multiplication are done in this environment. This is sufficient, because a group with addition and multiplication is already touring complete, so there is no need for any other operation.\\

>>>>

\subsection{Shamirs Secret Sharing Scheme}
This paper will not further discuss the family of garbled circuit protocols, but rather the second family which are protocols based on so called Linear Secret Sharing. 
These type of protocols were introduced by Adi Shamir at a similar time, in 1979 \cite{Shamir:1979:SS:359168.359176}.\\
The basic idea of this approach is that multiple parties split their secrets into so called shares and then distribute them to the other parties. In Shamir's scheme this is done by generating random polynomials with a degree depending on the security level and then calculating the shares as points in this polynomial. Computations are executed on these shares, and at the end it is possible to reconstruct the result from the different shares without revealing information about the initial secrets. This is done by using Lagrange interpolation.\\
 There is a huge family of protocols build on this approach, and it is still evolving every day. This paper will focus on the newest of these protocols that were developed in the last 10 years, especially on the protocols which are based on or similiar to SPDZ.\\

@@

\subsubsection{Secret sharing}

As mentioned before, SCALE-MAMBA, and in general similiar protocols like SPDZ, use linear secret sharing.\\
Given party \(P_i\) which holds a secret value \( a \in \mathcal{F}_p\) and a share of the global MAC key \( \alpha\). Then \( P_i\) can additvely share \( a\) with the other \(n-1\) parties as follows:
\begin{itemize}
\item Choose random \(\delta_a \in \mathcal{F}_p\)
\item Compute tag $ \gamma (a)= \alpha(a+\delta)$
\item Choose random \(a_1,...,a_n \in \mathcal{F}_p\) so that $ a=(a_1+...+a_n)$
\item Choose random \((\gamma (a)_1+...+\gamma (a)_n) \in \mathcal{F}_p\) so that $\gamma (a)=((\gamma (a)_1+...+\gamma (a)_n))$
\item Send to each party \( P_j \) \( \delta_a \) and the shares \(a_j \) and, \( \gamma (a)_j \)
\item Now party \( P_j\) holds a share of \( a\) as tuple \(\langle a_i\rangle = (\delta_a,a_i,\gamma(a)_i )\)
\end{itemize}

In SCALE-MAMBA, this value is then represented as followin tuple:\\
$\langle a\rangle=(\delta_a, (a_1,...,a_n),(\gamma (a)_1,...,\gamma (a)_n))$
\\With:
\begin{itemize}
\item $ a=(a_1+...+a_n)$
\item $ \gamma (a)=((\gamma (a)_1+...+\gamma (a)_n))=\alpha(a+\delta)$
\item Every party \( P_i\) holds a share of \( a\) as tuple \(\langle a_i\rangle = (\delta_a,a_i,\gamma(a)_i )\)

 and the corresponding tag \( \gamma(a)\). Then th
Sharing of values:\\
After sharing a value \( a \in F_p\), it is represented as following tuple:\\
$\langle a\rangle=(\delta_a, (a_1,...,a_n),(\gamma (a)_1,...,\gamma (a)_n))$
\\With:
\begin{itemize}
\item $ a=(a_1+...+a_n)$
\item $ \gamma (a)=((\gamma (a)_1+...+\gamma (a)_n))=\alpha(a+\delta)$
\item Every party \( P_i\) holds a share of \( a\) as tuple \(\langle a_i\rangle = (\delta_a,a_i,\gamma(a)_i )\)

@@

Now it is assumed that the offline phase was succesfully executed, so all preliminaries are given to execute the online phase. It's main goal is to evaluate a specified circuit with secret inputs by the different parties. So this is the heart of the system, the part where the real computatiuon is executed. \\
It is important to note, that the online phase is nearly perfectly optimized when assuming the offline phase was carried out succesfully. The online phase has a runtime complexity in O(n), and therefore there is not a really big performance impact. It is also noteworthy, that in the online phase only computational and no information theoretical problems are solved. All this leads to the fact, that there is not really any change in the online phase in the SPDZ like protocols in the last years, therefore the online phase is the same like in the earlier version of SPDZ  ~\cite{cryptoeprint:2011:535}.\\

@@

Following, it is going to be demonstrated, how addition and multiplication are done in this environment. This is sufficient, because a group with addition and multiplication is already touring complete, so there is no need for any other operation.  Furthermore, addition and multiplications with constants are also discussed.\\
